The pollination trade-off

### 2018-12-08 paper/manuscript.Rmd
request feedback question three framing in intro
Improved first paragraph of discussion

* Journal?
* Do you know of a reasonable reference for the claims in \lr{ref-needed-possitive-loops} and \lr{ref2}?
* I got feedback that "denote" in \lr{denote} might be overly formal? 
* Hugo. Some journals require publication of data alongside with the paper. Is it OK to consider those? Or you prefer to keep data private?
* In Figure \@ref(fig:fig-trade-off-predictions)a, I determine if the slope is significantly positive or negative by checking whether the standard errors cross 0. Should it be 2 times SE? Should all other error bars in Figure \@ref(fig:fig-trade-off-predictions) be 2 times SE?
* What do you think about the quantity/quality discourse now? I'm still unconvinced. Maybe I should just go for relationship conspecific/heterospecific instead of quality? That would mean that Figure \@ref(fig:fig-average-qual-quant)c would just need the right panel. Cause the left is just almost the same as Figure \@ref(fig:fig-average-qual-quant)b, except that it includes models in which the variable was not present and hence "shrinks" the model averaged estimate.  
* Unsure of whether in Figure \@ref(fig:fig-pca)a, it would be better to display the contribution of each component to total variance instead of the cummulative contribution.

@@

>>>>

* Journal?
* Do you know of a reasonable reference for the claims in \lr{ref-needed-possitive-loops} and \lr{ref2}?
* Hugo. Some journals require publication of data alongside with the paper. Is it OK to consider those? Or you prefer to keep data private?
* In Figure \@ref(fig:fig-trade-off-predictions)a, I determine if the slope is significantly positive or negative by checking whether the standard errors cross 0. Should it be 2 times SE? Should all other error bars in Figure \@ref(fig:fig-trade-off-predictions) be 2 times SE?
* What do you think about the quantity/quality discourse now? I'm still unconvinced. Maybe I should just go for relationship conspecific/heterospecific instead of quality? That would mean that Figure \@ref(fig:fig-average-qual-quant)c would just need the right panel. Cause the left is just almost the same as Figure \@ref(fig:fig-average-qual-quant)b, except that it includes models in which the variable was not present and hence "shrinks" the model averaged estimate.  
* Unsure of whether in Figure \@ref(fig:fig-pca)a, it would be better to display the contribution of each component to total variance instead of the cummulative contribution.
* I'm not very happy with the way the third hypothesis is described in the intro (\lr{third-hypothesis}). I would appreciate ideas to rephrase it clearly

@@

Our results suggest that the community context plays a central role at determining competition for pollination. 
First, we found that the costs of pollinator sharing are pervasive. In particular, we found that a significant proportion of species undergoes overall neutral or competitive effects from animal mediated pollination. 
Second, we found that plants are able to minimise the intensity of this competition using multiple strategies, however, conspecific and heterospecific pollen deposition are tightly coupled and threfore these strategies are likely to involve a trade-off between the quantity and quality of pollination. 
Third, we found that these strategies are strongly shaped by the community context, this is, the same plant species can adopt dramatically different strategies depending on the comminity it belongs to.
